### 2020-12-18 paper/sex_selection_spacing-ver5.tex
Add guidepost for empirical strategy

The standard approach in the birth spacing literature is to use proportional hazard
models with a single exit---the birth of a child.%
\footnote{
See \citet{Sheps1970} and \citet{Newman1984} for early discussions of why 
hazard models are the preferred way to deal with the censoring of birth
intervals.
}
There are two problems with the standard approach in this setting.

>>>>

The empirical analysis has three parts. 
First, I document the changes in birth spacing over time and how the introduction of sex 
selection influenced birth spacing. 
Second, I compare period fertility estimates with predicted cohort fertility based on the 
model of birth spacing. 
Finally, I examine how birth intervals affect infant mortality and whether the apparent 
increase in sex selection influenced mortality.

This section presents the empirical model for my analysis of birth spacing. 
The standard approach in the birth spacing literature is to use proportional hazard
models with a single exit---the birth of a child.%
\footnote{
See \citet{Sheps1970} and \citet{Newman1984} for early discussions of why 
hazard models are the preferred way to deal with the censoring of birth
intervals.
}
There are two problems with the standard approach in this setting.
